Verifying Cache Coherence Protocols for an infinite set of cache hierarchies

### 2014-02-06 paper/Abstract.tex
this the the correct version

Correct implementation of cache coherent systems is of high importance in
industrial use. We first provide a concise mathematical definition of a cache
coherent system as one which obeys store atomicity. We give a Coq-based proof
of an MSI cache coherence protocol for an infinite set of cache hierarchies. We
specify a set of invariants which imply store atomicity, enabling other
protocols to be verified for store atomicity automatically as long as they
satisfy the invariants. Our key insight for proving these invariants is a set
of fundamental properties.  We believe that these fundamental properties are
true for many other invalidation-based protocols with no silent drops -- we
show that informally for MESI, MOSI and MOESI protocols.

>>>>

Correct implementation of cache coherent systems is of high importance in
industrial use. We first provide a concise mathematical definition of a cache
coherent system as one which obeys store atomicity. We give a Coq-based proof
of an MSI cache coherence protocol for an infinite set of cache hierarchies. We
specify a set of invariants which imply store atomicity, enabling other
protocols to be verified for store atomicity automatically as long as they
satisfy the invariants. Our key insight for proving these invariants is a set
of fundamental properties.  We believe that these fundamental properties hold
for many other invalidation-based protocols with no silent drops -- we show
that informally for MESI, MOSI and MOESI protocols.
